---
title: "Spotilytics Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(spotilytics)
data('rb')
```

### How to get properly formatted data for spotilytics:

1) Visit [Exportify](https://exportify.net/).

2) Log in with your Spotify SSO. 

3) Choose your favorite playlist and click download .csv.

4) Load your playlist data into RStudio.

### How to use `favorite_artists()` Function:

After loading in playlist data from Exportify, you may see your top 6 artists within this playlist like so:

```{r}
favorite_artists(rb)
```
If you would like to see your "least favorite" artists (or at least the ones who appear the least in your playlist), change the `ascending` argument to `TRUE`.

```{r}
favorite_artists(rb, ascending=TRUE)
```

If you want to see more of your favorite artists, use the `count=` argument

```{r}
favorite_artists(rb, count=10)
```

To just return the whole dataframe, set the `see_all` argument to `TRUE`.

```{r}
all_artists <- favorite_artists(rb, see_all=TRUE)

all_artists
```

